Quantum Computing and its Implications on Digital Security

### 2021-12-12 paper.tex
feat: Improve nuclear magnetic resonance

% Add page numbers to papers
% Where I make references, put actual hyperlinks

@@

Since Paul Benioffs and Richard Feynman's talks on quantum computing held at the first conference on the physics of computation, 
quantum computing has become a large research area. 
Even so large, that is has become more and more difficult to understand the basics of it and its implications on the future of computing. 
This work will introduce the reader to the basics of quantum computing from a computer scientists perspective. 
Hence this paper focuses on the computer scientists perspective, it is important to look at the implications on digital security, especially cryptography.

@@

\begin{section}{Quantum Computers}
Quantum computers utilize qubits to represent information. 
Instead of working with a stream of electiral or optical signals representing 1s and 0s, 
quantum computers utilize qubits, which can represent various combinations of 1s and 0s at the same time. 
This effect is called superposition. To put qubits into superposition, 
researchers manipulate qubits in different ways. As quantum computing is based on quantum mechanics and hence has to obey to the same laws, 
a measurement determines the state of a qubit. Once qubits are measured, 
it's quantum state immediately collapses to either 1 or 0 and its state of superposition is lost.

@@

\begin{subsection}{Nuclear Magnetic Resonance}
A Nuclear Magnetic Resonance (NMR) computer consists of a capsule filled with a liquid and an NRM machine. 
Each molecule in the liquid is an independet quantum memory register. 
Computation proceeds by sending radio pulses to the sample and reading its response. 
Qubits are implemented as spin states of the nuclei of atoms comprising the molecules. 
In contrast to the Ion Trap computer, 
a measurement is performed on a statistical ensemble of molecules instead of a single isolated quantum system which was used as memory register. 
NMR computers have been achieving the most accomplishements in quantum computing so far, 
as they can solve non-polynomial complete problems in a polynomial time.

Initially the approach was to use the soin properties of atoms of particular molecules in a liquid sample as qubits - 
this is known as liquid state NMR (LSNMR). 
This approach has since been superseeded by solid state NRM (SSNMR) as a means of quantum computation.

Solid state NMR (SSSNMR) differs from LSNMR in that we have a solid state sample, 
for example a nitrogen vacancy diamond lattice rather than a liquid sample. 
This has many advantages such as lack of molecular diffusion coherence, 
lower temperatures can be achieved to the point of suppressing phonon decoherence and a greater variety of control operations that allow us to overcome one of the major problems of LSNMR that is initialisation. 
Moreover, as in a crystal structure we can localize precisely the qubits, 
we can measure each qubit individually, 
instead of having an ensemble measurement as in LSNMR.

More recent work shows that all experiments in liquid state bulk ensemble NMR quantum computing to date do not possess quantum entanglement, 
thought to be required for quantum computation. 
Hence NMR quantum computing experiments are likely to have been only classical simulations of a quantum computer. 
\end{subsection}

>>>>

@@

Since Paul Benioffs and Richard Feynman's talks on quantum computing held at the first conference on the physics of computation, 
quantum computing has become a large research area. 
Even so large, that is has become more and more difficult to understand the basics of it and its implications on the future of computing. 
This work will introduce the reader to the basics of quantum computing from a computer scientists perspective. 
Hence it is important to look at the implications on digital security, especially cryptography.

@@

\begin{section}{Quantum Computers}
Quantum computers utilize qubits to represent information. 
Instead of working with a stream of electiral or optical signals representing 1s and 0s, 
quantum computers utilize qubits, which can represent various combinations of 1s and 0s at the same time. 
This effect is called superposition. To put qubits into superposition, 
researchers manipulate qubits in different ways. As quantum computing is based on quantum mechanics and hence has to obey to the same laws, 
a measurement determines the state of a qubit. Once qubits are measured, 
its quantum state immediately collapses to either 1 or 0 and its state of superposition is lost.

@@

\begin{subsection}{Nuclear Magnetic Resonance}
As explained in the article by Gershenfeld \cite{Gershenfeld1998QuantumCW}, a nuclear magnetic resonance (NMR) computer consists of a capsule filled with a liquid and an nuclear magnetic resonance spectrometer which is a machine used to analyze the molecular structure of a material by measuring the interaction of nuclear spins when placed in a strong magnetic field.
Each molecule in the liquid represents an quantum memory register. 
NMRs can compute by sending radio signals to the sample using the NMR machine and evaluating the response. 
In an NMR quantum computer, qubits are represented as spin states of the atoms in the molecules. 
In contrast to the ion trap quantum computer, 
a measurement is performed on a statistical ensemble of molecules instead of a single isolated quantum system which was used as memory register.

Initially, as mentioned above, the NMRs used atoms in a liquid sample as qubits which is known as liquid state NMR (LSNMR). 
Since solid state NMRs (SSNMR) emerged, SSNMR is usually preferred in terms of performing quantum computation.

Solid state NMR (SSSNMR) differ from LSNMR in that SSSNMR provide a solid state sample.
This has many advantages such as lack of molecular diffusion coherence and lower temperatures, as well as the more precise localization of qubits using crystal structures.
In SSNMRs, qubits can be measured individually, same as in the ion trap,
instead of having to measure an ensemble of molecules as in LSNMR.

NMRs have been succesfully used in quantum computing, as they can solve non-polynomial problems in a polynomial time.
According to Gershenfeld \cite{Gershenfeld1998QuantumCW}, the first successful computation on a NMR quantum computer was to execute a search using Grover's algorithm, 
which will be covered in the respective chapter. 
\end{subsection}
